A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex

@@

\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
& & & & \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
}
\]
These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
\[
S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
\]
The odd part of the $\cN=2$ supersymmetry algebra is 
\[
\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
\]
where $W_+$ is a complex two-dimensional symplectic vector space. 
From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $\alpha_+$ is a basis element for $S_+^2$. 
%A general supercharge $Q \in S_+^4 \otimes W$ is of the form
%\[
%Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
%\]
%where $s_+, s_+' \in S_+^{4}$.

Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
We twist by a supercharge of the form
\begin{equation} 
\label{eq:4dHodgefamily}
Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
\end{equation}
where $t \in \CC$. 
When $t \ne 0$, this supercharge is of rank $(2,0)$. 
At $t = 0$ it reduces to the holomorphic supercharge from the previous section.

Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
Denote by $L\subset V$ the $i$-eigenspace of the complex structure determined by the holomorphic supercharge $Q_0$. 
We utilize the same notation for the fields of super Yang-Mills theory as in the previous section. 
\brian{discuss twisting homomorphism}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}
\begin{proof}
We first write down the fields and the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}
The anti-fields decompose in an analogous way.

For a general supercharge $Q_+ \otimes \alpha_+ \in S_+^4 \otimes W = S^4_+ \otimes W_+ \otimes S_+^2$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*) + (\rho(\d_A a)Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \dvol (((Q_+,\psi_+), \phi^*) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)) \\
I^{(2)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_+^*,\lambda_+^*) - \frac 12  (Q_+, \lambda_+^*)^2 - (Q_+,Q_+) a c^* \big) \\
I^{(2)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*) .
\end{align*}

The result follows from further decomposing the fields under the action of $\MU(2)$. 
\end{proof}

\begin{theorem}
The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U\ham g)_{\mr{Hod}})$. 
Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4dDonaldsontwist}
\end{theorem}
\begin{proof}
The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.

>>>>

Note that the $\MU(2)$-action on the fields factors through a $\U(2)$-action since the square roots $\det(L)^{1/2}$ have canceled out.

@@

\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
& & & & \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
}
\]
These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
\end{proof}

@@

Consider the same twisting homomorphism $\phi\colon \MU(2)\rightarrow G_R$ as in Section \ref{sect:4d_2_holomorphictwist} and $\alpha=\alpha_0\colon \U(1)\rightarrow G_R$. With respect to the $\MU(2)$-action we have a decomposition
\[S_+\otimes W\cong \CC Q_0 \oplus \det(L)^{-1}\oplus \CC \Bar{Q}_0\oplus \det(L).\]

Consider a family of supercharges
\begin{equation} 
\label{eq:4dHodgefamily}
Q_t = Q_0 + t \Bar{Q}_0
\end{equation}
where $t \in \CC$. When $t \ne 0$, this supercharge is of rank $(2,0)$, while at $t = 0$ it reduces to the holomorphic supercharge from the previous section.

\begin{remark}
With respect to $\alpha_n\colon \U(1)\rightarrow G_R$ the supercharge $Q_0$ has weight $1$, while $\Bar{Q}_0$ has weight $-4n+1$. So, requiring $Q_t$ to have weight $1$ forces us to choose $n=0$.
\end{remark}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
\end{align*}
\end{prop}

\begin{theorem}
The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, ((U\oplus \fg[2]) / \fg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4dDonaldsontwist}
\end{theorem}
\begin{proof}
The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.
